Trends of SDR in Thessaloniki

### 2023-11-04 MDPI_submition.Rmd
Commit 2023-11-04 19:09
Commit 2023-11-04 20:14

We have demonstrated that in the period
`r paste(year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)))`, there is a brightening trend of SDR for all-sky conditions ($`r alltrend`\,\%/y$).
On a previous study [@Bais2013], for the period 1993 - 2011 the trend was found to be $0.33\,\%/y$.
The increase of this trend, indicates that the phenomenon and probably the causes, are still occurring.
Accordingly, we found a similar trend for clear-sky conditions ($`r cleartrend`\,\%/y$) that further supports that the brightening can be independent of the cloud occurrences, although, cloud formation can also attenuate SDR.
We have calculated the effect of TSI variability to be a negligible factor in SDR variability.
Unfortunately, there is no available data for this period for the aerosols, in order to directly estimate their effect on SDR, which is the most probable main cause.
The attenuation of SDR by aerosols over Europe have been proposed as major factor by @Wild2021.
The dimming effect of SDR under cloud-sky condition ($`r cloudtrend`\,\%/y$), shows that clouds can also attenuate the amount of SDR reaching the ground, and changes on their occurrences can effect the net energy balance.
Because we have no adequate data to investigate the long term changes of cloud formation in the region, we can not infer if the SDR trend we observe under cloud-sky is biased by changes in clouds and local climate.
The observed brightening of SDR over Thessaloniki; is dependent on SZA (higher SZA, have stronger brightening trends), and also, with the seasons of the year, where Winter and Autumn show a significant strong trend, in contrast to Spring and Summer.
<!-- to conclutions? -->
Using CUSUMs of the trends for all- and clear-skies, we observed periods where the CUSUMs remain relative steady,
<!-- roughly around the middle of the study dataset,--> with a steep decline previous to that, and a steep incline after. This is an indication that the whole brightening phenomenon does not follow a smooth development over time.

>>>>

We have demonstrated that in the period
`r paste(year(min(ALL_1_daily_DESEAS$Date)), " - ", year(max(ALL_1_daily_DESEAS$Date)))`, there is positive trend in SDR of for all-sky conditions ($`r alltrend`\,\%/y$).
Α previous study [@Bais2013], for the period 1993 - 2011 the trend was found to be $0.33\,\%/y$.
The increase of this trend, indicates that the phenomenon and probably the causes, are still occurring.
Accordingly, we found a similar trend for clear-sky conditions ($`r cleartrend`\,\%/y$) that further supports that the brightening can be independent of the cloud occurrences, although, cloud formation can also attenuate SDR.
We have calculated the effect of TSI variability to be a negligible factor in SDR variability.
Unfortunately, there is no available data for this period for the aerosols, in order to directly estimate their effect on SDR, which is the most probable main cause.
The attenuation of SDR by aerosols over Europe have been proposed as major factor by @Wild2021.
The dimming effect of SDR under cloud-sky condition ($`r cloudtrend`\,\%/y$), shows that clouds can also attenuate the amount of SDR reaching the ground, and changes on their occurrences can effect the net energy balance.
Because we have no adequate data to investigate the long term changes of cloud formation in the region, we can not infer if the SDR trend we observe under cloud-sky is biased by changes in clouds and local climate.
The observed brightening of SDR over Thessaloniki; is dependent on SZA (higher SZA, have stronger brightening trends), and also, with the seasons of the year, where Winter and Autumn show a significant strong trend, in contrast to Spring and Summer.
<!-- to conclutions? -->
Using CUSUMs of the trends for all- and clear-skies, we observed periods where the CUSUMs remain relative steady,
<!-- roughly around the middle of the study dataset,--> with a steep decline previous to that, and a steep incline after. This is an indication that the whole brightening phenomenon does not follow a smooth development over time.

### 2023-11-04 MDPI_submition.tex
Commit 2023-11-04 20:14

We have demonstrated that in the period 1993 - 2023, there is a
brightening trend of SDR for all-sky conditions (\(0.38\,\%/y\)). On a
previous study \citep{Bais2013}, for the period 1993 - 2011 the trend
was found to be \(0.33\,\%/y\). The increase of this trend, indicates
that the phenomenon and probably the causes, are still occurring.
Accordingly, we found a similar trend for clear-sky conditions
(\(0.35\,\%/y\)) that further supports that the brightening can be
independent of the cloud occurrences, although, cloud formation can also
attenuate SDR. We have calculated the effect of TSI variability to be a
negligible factor in SDR variability. Unfortunately, there is no
available data for this period for the aerosols, in order to directly
estimate their effect on SDR, which is the most probable main cause. The
attenuation of SDR by aerosols over Europe have been proposed as major
factor by \citet{Wild2021}. The dimming effect of SDR under cloud-sky
condition (\(-0.28\,\%/y\)), shows that clouds can also attenuate the
amount of SDR reaching the ground, and changes on their occurrences can
effect the net energy balance. Because we have no adequate data to
investigate the long term changes of cloud formation in the region, we
can not infer if the SDR trend we observe under cloud-sky is biased by
changes in clouds and local climate. The observed brightening of SDR
over Thessaloniki; is dependent on SZA (higher SZA, have stronger
brightening trends), and also, with the seasons of the year, where
Winter and Autumn show a significant strong trend, in contrast to Spring
and Summer. Using CUSUMs of the trends for all- and clear-skies, we
observed periods where the CUSUMs remain relative steady, with a steep
decline previous to that, and a steep incline after. This is an
indication that the whole brightening phenomenon does not follow a
smooth development over time.

>>>>

We have demonstrated that in the period 1993 - 2023, there is positive
trend in SDR of for all-sky conditions (\(0.38\,\%/y\)). Α previous
study \citep{Bais2013}, for the period 1993 - 2011 the trend was found
to be \(0.33\,\%/y\). The increase of this trend, indicates that the
phenomenon and probably the causes, are still occurring. Accordingly, we
found a similar trend for clear-sky conditions (\(0.35\,\%/y\)) that
further supports that the brightening can be independent of the cloud
occurrences, although, cloud formation can also attenuate SDR. We have
calculated the effect of TSI variability to be a negligible factor in
SDR variability. Unfortunately, there is no available data for this
period for the aerosols, in order to directly estimate their effect on
SDR, which is the most probable main cause. The attenuation of SDR by
aerosols over Europe have been proposed as major factor by
\citet{Wild2021}. The dimming effect of SDR under cloud-sky condition
(\(-0.28\,\%/y\)), shows that clouds can also attenuate the amount of
SDR reaching the ground, and changes on their occurrences can effect the
net energy balance. Because we have no adequate data to investigate the
long term changes of cloud formation in the region, we can not infer if
the SDR trend we observe under cloud-sky is biased by changes in clouds
and local climate. The observed brightening of SDR over Thessaloniki; is
dependent on SZA (higher SZA, have stronger brightening trends), and
also, with the seasons of the year, where Winter and Autumn show a
significant strong trend, in contrast to Spring and Summer. Using CUSUMs
of the trends for all- and clear-skies, we observed periods where the
CUSUMs remain relative steady, with a steep decline previous to that,
and a steep incline after. This is an indication that the whole
brightening phenomenon does not follow a smooth development over time.
